---
title: "LAB1 STAT515"
author: "Mykola Signayevskyy"
date: "2023-02-03"
output:
  pdf_document: default
  html_document: default
---

#### a) Read in the "carseats" dataset, look at the first few rows and inspect the data types of the variables in the dataframe.

```{r}
carseats = read.csv('carseats.csv')
head(carseats)
str(carseats)
```

#### b) Change the variables "ShelveLoc, urban, US" into a factor variables.
```{r}
carseats$ShelveLoc=as.factor(carseats$ShelveLoc)
carseats$Urban=as.factor(carseats$Urban)
carseats$US=as.factor(carseats$US)
str(carseats) #checking changes 
```

#### c) create a new variable called "profit" which stands for "Income - Advertising"
```{r}
carseats$Profit = carseats$Income - carseats$Advertising
head(carseats$Profit) #checking result
```

#### d) Check for missing data. If you have missing data remove the corresponding rows from the dataset.
```{r}
table(is.na(carseats))
carseats = na.omit(carseats)
table(is.na(carseats)) #checking result
```

#### e) How many "Good" shelving locations are there in the dataset?
```{r}
length(which(carseats$ShelveLoc=='Good'))
```

#### f) How many stores are inside the USA? create a separate data frame containing all stores from USA. #name the data set as "stores_USA"
```{r}
length(which(carseats$US=="Yes"))

stores_USA = carseats[carseats$US=='Yes',]
head(stores_USA)
```

#### g) create another data set called "HighUrban_USSales" using 'stores_USA' data set. #where, sales are greater than 7 thousand and stores are located in Urban areas.
```{r}
HighUrban_USSales = subset(stores_USA, Sales > 7 & Urban == "Yes")
head(HighUrban_USSales)
```

#### h) Remove "US" and "Urban" columns from the "HighUrban_USSales" dataset.
```{r}
HighUrban_USSales = subset(HighUrban_USSales, select = -c(Urban , US))
head(HighUrban_USSales)
```
#### i) For one the above subset, write to a new CSV file
```{r}
write.csv(HighUrban_USSales, "HighUrban_USSales.csv")
```

